### 2019-03-08 Appendices/AppendixE.tex
Figure2 changes

\begin{equation}
\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}
\end{equation}

@@

>>>>

\begin{equation}
\label{FloquetMode}
\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}
\end{equation}

@@

\section{Extended Hilbert space}

Having introduced the micromotion operator and the Floquet Hamiltonian, we turn on to introduce the concept of extended Hilbert space. Introducing \ref{FloquetMode} in the Scr\"{o}dinger equation we get:

\begin{equation}
\left[ \hat{H}-i\text{d}_t\right] \ket{u_n(t)} = \epsilon_n\ket{u_n(t)}
\end{equation}

This can be regarded as an eigenvalue problem in the space $\mathcal{F}=\mathcal{H}\otimes\mathcal{L}_T$, where $\mathcal{L}_T$ is the space of square integrable T-periodic functions. The operator $\hat{Q} = \hat{H}-i\text{d}_t$ acting on $\mathcal{F}$ is referred to as the quasienergy operator. States in the extended Hilbert space (that is, a state plus its periodic time dependence) is usually denoted as $\ket{u}\rangle$, and the inner product in this space is defined as:

\begin{equation}
\langle \bra{u}\ket{v} \rangle = \frac{1}{T}\int_0^T \text{d}t \bra{u(t)}\ket{v(t)}
\end{equation}

An orthonormal basis for the extended Hilbert space can be obtained as the direct product an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$. A convenient orthonormal basis for $\mathcal{L}_T$ is given by the functions $e^{im\omega t}$, therefore, if $\ket{\alpha}$ labels an orthonormal basis of $\mathcal{H}$, then the set of functions $\ket{\alpha m (t)} = \ket{\alpha}e^{im\omega t}$ is a basis of the extended Floquet space, and it is denoted as $\ket{\alpha m}\rangle$. In this basis, the quasienergy operator has matrix elements:

\begin{align}
\langle \bra{\alpha' m'}\hat{Q}\ket{\alpha m} \rangle &= \frac{1}{T}\int_0^T \text{d}t e^{-im'\omega t}\bra{\alpha'} \hat{H}(t)-i\hbar\text{d}_t \ket{\alpha}e^{im\omega t} = \nonumber \\
&= \bra{\alpha'} \hat{H}_{m'-m} \ket{\alpha} + \delta_{m'm}\delta_{\alpha' \alpha}m\hbar\omega \label{QOmatelem}
\end{align}

Where
\begin{equation}
\hat{H}_m = \frac{1}{T}\int_0^T \text{d}t e^{-im\omega t}\hat{H}(t) 
\end{equation}
is the Fourier transform of the Hamiltonian. Now, a Floquet state $\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}$ can be expanded as $\ket{u_n(t)} = \sum_m e^{im\omega t}\ket{u_{nm}}$, using \ref{QOmatelem} and projecting onto the \textit{m}th Fourier mode we can rewrite the Scr\"{o}dinger equation as:

\begin{equation}
(\epsilon_n+m\omega)\ket{u_{nm}} = \sum_{m'}\hat{H}_{m-m'}\ket{u_{nm'}}
\end{equation}
